%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {Co-Founder \& Vice-President} % Job title
      {PoliMovies Cinematography \& Film Making Association} % Organization
      {Milan, Italy} % Location
      {Jun. 2023 - Present} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          {PoliMovies is the first designers-led student association at Politecnico di Milano, \\dedicated to creating a vibrant community of aspiring filmmakers and cinephiles. \\Our mission is to promote cinematography culture to students through curated movie screenings and cine forums, hands-on workshops to develop storytelling and film production skills, and collaborative production projects. We provide opportunities for members to explore the art and craft of filmmaking, develop their skills, and showcase their creative talents.}
          \item {}
          \item {Coordinated licensing agreement for the screening of movies}
          \item {Managing relations with entities and brands collaboration for the organization of events}
          \item {Producer and Post Production Supervisor for the projects led by the association}
        \end{cvitems}
      }
  
  %---------------------------------------------------------
    \cventry
      {Student Ambassador} % Job title
      {Politecnico di Milano} % Organization
      {Milan, Italy} % Location
      {Apr. 2023 - Present} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Counseling students in discovering the field of Digital and Interaction Design and getting to know life at Politecnico di Milano}
        \end{cvitems}
      }
  
  %---------------------------------------------------------
    \cventry
      {UI Designer} % Job title
      {Softec S.p.A.} % Organization
      {Milan, Italy} % Location
      {May. 2022 - Jul. 2022} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          {Internship in the Marketing and Design department of the company}
          \item {}
          \item {Assisted the Design team in transitioning from Sketch to Figma}
        \end{cvitems}
      }
  
  %---------------------------------------------------------
    \cventry
      {IT Consultant \& Innovative Technologies Tutor} % Job title
      {Politecnico di Milano} % Organization
      {Milan, Italy} % Location
      {Mar. 2021 - Dec. 2021} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          {Collaboration with METID department in Politecnico di Milano assisting schools during the COVID-19 pandemic with distance learning, \\counseling teachers and students in the use of digital and innovative learning platforms}
          \item {}
          \item {Performed programming lessons in an elementary school utilizing a tailored educational version of the popular video game Minecraft}
        \end{cvitems}
      }
  
  %---------------------------------------------------------
  \end{cventries}
